Chaotic mixing of tidal debris

### 2015-06-25 ms.tex
new results section

This paper is organized as follows. We review relevant nonlinear dynamics in Section~\ref{sec:nldreview}. In Section~\ref{sec:methods}, we describe our choice of potential, method for numerical orbit integration, and introduce the chaos indicators used in this work. Our results are split into three subsections: in Section~\ref{sec:results1} we present iso-energy grids of orbits and discuss the orbit classes and chaotic timescales present in our potential; in Section~\ref{sec:results2} we study the density evolution of small ensembles of orbits around each orbit of the previous section; and, in Section~\ref{sec:results3} we describe the behavior of chaotic diffusion and use this to explain how chaos is relevant for tidal streams over short times. We discuss the implications of our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.

@@

>>>>

This paper is organized as follows. We review relevant nonlinear dynamics in Section~\ref{sec:nldreview}. In Section~\ref{sec:methods}, we describe our choice of potential, method for numerical orbit integration, and introduce the chaos indicators used in this work. Our results are split into four subsections: in Section~\ref{sec:results1} we present iso-energy grids of orbits and discuss the orbit classes and chaotic timescales present in our potential; in Section~\ref{sec:results2} we study the density evolution of small ensembles of orbits around each orbit of the previous section; in Section~\ref{sec:results3} we describe the behavior of chaotic diffusion and use this to explain how chaos is relevant for tidal streams over short times; and in Section~\ref{sec:results4} we propose a new indicator for evaluating whether chaotic diffusion of orbits will be important for the morphological evolution of tidal debris. We discuss the implications of our results in Section~\ref{sec:discussion}, and conclude in Section~\ref{sec:conclusions}.

@@

\subsection{Part IV: Proposed indicator of chaotic density evolution}\label{sec:results4}
